|

### 2023-05-15 paper/04-results.Rmd
more edits.

[^unsuccess]: A real-game footage of this play is available at https://www.nfl.com/videos/teddy-bridgewater-courtland-sutton-barely-miss-out-on-chance-at-62-yard-td-bomb

@@

Our results show many true positives with no surprises.
Myles Garrett and TJ Watt are known as top-tier edge rushers, while Aaron Donald is undoubtedly the best interior defender in football.
Rashan Gary, a young rusher with huge potential, ranks first among all pass rushers according to our metric.
Moreover, our leaderboards largely match the rankings of experts in the field.
For instance, there is considerable overlap between our lists and PFF's edge [@Monson2022nfl] and interior [@Linsey2022nfl] rusher rankings released after the 2021 season.
This ultimately lends credibility to our proposed metric STRAIN as a measure of pass rushing effectiveness.

@@

Next, we examine different statistical properties of our proposed metric STRAIN.
Our focus here is to understand the stability and predictability of STRAIN, and we pose the following question:
How much does our metric vary from week to week?
In other words, is previous performance predictive of future performance based on our metric?
Below, we attempt the answer these questions, and the following results are for pass rushers with at least 100 snaps played during the first 8 weeks of the 2021 NFL regular season.

@@

In addition to adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN.
Figure \ref{fig:fig_rankings_boot} displays the mean varying intercept for the top ten pass rushers for each position along with 95% confidence intervals. 
We observe similar rankings based on the random intercepts in comparison to the average STRAIN results in Tables \ref{tab:edge} and \ref{tab:interior}, with Myles Garrett (DE), Aaron Donald (DT), Vita Vea (NT), and T.J. Watt (OLB) as the top pass rusher for their respective position. 
We observe different levels of variability across these top players, with the only a subset of players with intervals strictly above zero. This is not necessarily surprising given the limited sample of data. Additionally, we are ignoring correlated performance between pass rushers on the same team.
For instance, the top two defensive ends, Myles Garrett and Takkarist McKinley (see the top panel of Figure \ref{fig:fig_rankings_boot}), are teammates on the Cleveland Browns.
McKinley is a surprising name in our list and we suspect that his high rank is mostly due to playing on the same defensive unit with Garrett, who is well-known as an elite pass rusher.
We leave the exploration of adjusting for teammates for future work.

>>>>

[^unsuccess]: Game footage of this play is available at https://www.nfl.com/videos/teddy-bridgewater-courtland-sutton-barely-miss-out-on-chance-at-62-yard-td-bomb

@@

<!-- Our results show many true positives with no surprises. -->
Our results are mostly consistent with conventional rankings of rushers.  For instance, Myles Garrett and TJ Watt are known as top-tier edge rushers and both show up in our top ten edge rushers. Additionally, Aaron Donald is nearly universally considered the best interior defender in football, and he appears at the top of our rankings of interior rushers.   
<!-- Rashan Gary, a young rusher with huge potential, ranks first among all pass rushers according to our metric over the period of time observed. -->
Moreover, our leader boards largely match the rankings of experts in the field.
For instance, there is considerable overlap between our lists and PFF's edge [@Monson2022nfl] and interior [@Linsey2022nfl] rusher rankings released after the 2021 season.
This ultimately lends credibility to our proposed metric STRAIN as a measure of pass rushing effectiveness.

@@

Next, we examine different statistical properties of our proposed metric STRAIN.
Our focus here is to understand the stability and predictability of STRAIN, and we pose the following question:
How much does our metric vary from week to week?
In other words, is previous performance as measured by our metric predictive of future performance based on our metric?
Below, we attempt the answer these questions, and the following results are for pass rushers with at least 100 snaps played during the first 8 weeks of the 2021 NFL regular season.

@@

In addition to adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN.
Figure \ref{fig:fig_rankings_boot} displays the mean varying intercept for the top ten pass rushers for each position along with 95% confidence intervals. 
We observe similar rankings based on the random intercepts in comparison to the average STRAIN results in Tables \ref{tab:edge} and \ref{tab:interior}, with Myles Garrett (DE), Aaron Donald (DT), Vita Vea (NT), and T.J. Watt (OLB) as the top pass rusher for their respective position. 
We observe different levels of variability across these top players, with only a subset of players with intervals strictly above zero. This is not necessarily surprising given the limited sample of data. Additionally, we are ignoring correlated performance between pass rushers on the same team.
For instance, the top two defensive ends, Myles Garrett and Takkarist McKinley (see the top panel of Figure \ref{fig:fig_rankings_boot}), are teammates on the Cleveland Browns.
McKinley is a surprising name on our list and we suspect that his high rank is mostly due to playing on the same defensive unit with Garrett, who is well-known as an elite pass rusher.
We leave the exploration of adjusting for teammates for future work.
